\documentclass{exam}


\begin{document}


**Student Chemistry Interest Survey**

This survey is designed to understand your interest and experience in chemistry. Your honest responses will help us improve the chemistry learning experience. All answers are anonymous.

**Part 1: General Interest in Chemistry**

\begin{questions}
    
\question How much do you enjoy learning chemistry?  
\begin{checkboxes}
    \choice A lot  
    \choice Somewhat  
    \choice Neutral  
    \choice Not much  
    \choice Not at all
\end{checkboxes}

\question How confident are you in your ability to understand chemistry concepts?  
\begin{checkboxes}
    \choice Very confident  
    \choice Confident  
    \choice Somewhat confident  
    \choice Not confident
\end{checkboxes}


\question How interested are you in pursuing further chemistry-related courses in the future?  
\begin{checkboxes}
    
    \choice Very interested  
    \choice Somewhat interested  
    \choice Neutral  
    \choice Not interested
\end{checkboxes}

\question How relevant do you think chemistry is to your daily life?  
\begin{checkboxes}
    \choice Very relevant  
    \choice Somewhat relevant  
    \choice Neutral  
    \choice Not relevant at all
\end{checkboxes}
   
   **Part 2: Chemistry Learning Experience**

\question Which aspect of chemistry do you enjoy the most? (Select all that apply)  
   \begin{checkboxes}
   \choice Experiments and lab work  
   \choice Learning about chemical reactions  
   \choice Studying the periodic table  
   \choice Real-world applications of chemistry  
   \choice Other:
\end{checkboxes}
   
\question How often do you participate in class discussions or ask questions during chemistry lessons?  
   \begin{checkboxes}
   \choice Always  
   \choice Often  
   \choice Sometimes  
   \choice Rarely  
   \choice Never
\end{checkboxes}
   
\question How helpful do you find chemistry homework and assignments in improving your understanding?  
\begin{checkboxes}
    \choice Very helpful  
    \choice Somewhat helpful  
    \choice Neutral  
    \choice Not very helpful
\end{checkboxes}
   
\question What type of learning activity helps you understand chemistry the best?  
\begin{checkboxes}  
\choice Hands-on experiments  
   \choice Group discussions  
   \choice Visual aids (diagrams, videos)  
   \choice Reading textbooks or articles  
   \choice Other:
\end{checkboxes}

**Part 3: Future Goals and Aspirations**

\question Do you see yourself pursuing a career related to chemistry or science in the future?
\begin{checkboxes}  
   \choice Definitely  
   \choice Possibly  
   \choice Unsure  
   \choice Probably not  
   \choice Definitely not
\end{checkboxes}
   
\question Which careers or fields of study are you interested in? (Select all that apply)  
   \begin{checkboxes}
   \choice Medicine  
   \choice Engineering  
   \choice Environmental Science  
   \choice Biochemistry  
   \choice Teaching  
   \choice Other:
\end{checkboxes}

**Part 4: Feedback and Suggestions**

\question What is one thing you like about your chemistry class?  

\question What is one thing you would change about your chemistry class to make it more interesting?  

\question Do you have any suggestions for improving chemistry learning in the classroom?  

\end{questions}

**Thank you for completing this survey! Your responses are valuable in helping us improve the learning experience in chemistry.**

\end{document}